\documentclass{resume}
\renewcommand{\categoryfont}{\sc}
\usepackage[final]{pdfpages}
\usepackage{bibunits}

\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
%
\addtolength{\marginparwidth}{-\marginparsep}
\setlength{\evensidemargin}{\oddsidemargin}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\addtolength{\textwidth}{-2\oddsidemargin}
\addtolength{\textwidth}{\marginparwidth}
\addtolength{\textwidth}{\marginparsep}
%
\setlength{\topmargin}{-0.5in}
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Ketan C Maheshwari}
% ------ Address --------------------------------------------------------

\address{\mbox{\small\tt ketancmaheshwari@gmail.com}\\
 	 \mbox{\small\tt km0@ornl.gov}\\
	}{646 Deanwood Ln,\\
	Knoxville,\\ TN 37934 USA\\}	
\begin{document}
% \includepdf[pages=1-1]{cover_letter.pdf}
\maketitle


%--------------------------------objective-----------------------------------------------------
\begin{category}{Objective}
\citemnobullet To work on challenges pertaining to HPC systems.
\end{category}

% ---------------------------------- Work experience ---------------------------------------------

\begin{category}{Work Experience}
\citem{Linux Systems Engineer} Oak Ridge National Laboratory, 2017 - current.

\citem{HPC Consultant} Center for Research Computing, University of Pittsburgh, 2016 - 2017.
Application development and deployment, source code debugging, expert and dedicated HPC user support,
implementation and management of Petabyte ZFS storage system, gave workshops on R, CUDA, advanced Linux and Python.

\citem{Postdoctoral Researcher} Distributed Systems Lab, Argonne National
Laboratory, 2011 - 2016.\\
Supporting large-scale applications on HPC infrastructures, user-engagement
catalyst and researcher for HPC and HTC infrastructures. Main activities
include developing, deploying and running parallel applications over IBM BG/Q,
Cray XE6 and Intel supercomputers, clusters and clouds. Applications
include protein docking, fMRI image processing, energy systems,
seismology simulation, and power grid modelling. Funded by NSF, DOE and
NIH.

\citem{ICT Developer(L5)} Informatics Institute(IvI), University of
Amsterdam(UvA), 2006 to 2007.\\
Globus File Transfer integration to
achieve transfer of large number of big files between Academisch Medical
Centrum (AMC) and Storage Resource Broker (SRB) at SARA, Amsterdam. Integrated
with a Visual Resource Browser.

\end{category}

\begin{category}{Teaching Experience}
\citem{Workshops} given on Linux tools, R-programming and GPU computing at Center for Research Computing (CRC), University of Pittsburgh.
\citem{Tutorial} given on Swift Parallel Scripting at CCGrid Conference in 2013.
\citem{Courses} taught Operating Systems, Java and C++ courses to undergrad students during PhD at Univ of Nice. 
\citem{Seminar} on Linux Productivity Tools at the League of Professional System Administrators (LOPSA) East Tennessee.
\end{category}

%\newpage
% ------- Skills ------------------------------------------------------
\begin{category}{Skills}
\citembullet Linux, ranked top 4~\% of Linux StackExchange Community (Mar 2018)
\citembullet Competent in Python, C/C++, Bash, awk, sed, \LaTeX
\citembullet Practical knowledge in R, CUDA, MPI, openMP
\citembullet Expertise in HPC toolchains, compilers, debuggers, schedulers, storage, network
\end{category}

% ----------------------------- Education ------------------------------------------------------
\begin{category}{Education}
\citem{University of Nice at Sophia Antipolis}, France.\\
PhD with \textbf{Highest Honors}, January 2011.\\
Research on parallel workflow expression and enactment on large-scale
distributed computing infrastructures for data intensive applications under the
guidance of Dr.  Johan Montagnat. The projects relate to the field of
biomedical imaging. First, the `Cardiac Image Processing Application'
involving processing 4D (3D + time) images of cardiac motion cycle and
extracting quantitative information about myocardial movement. Second, the
`Drug Discovery Application' that dealt with in-silico docking of protein
molecules by filtering a million potential candidates based on their `docking
energy'.

%======================================================================================

\citem{University of Amsterdam}, Amsterdam, The Netherlands.\\
Research M.Sc.(NVAO-accredited) in Grid Computing, August 2007.\\
\textbf{Masters Thesis Work}\\
To achieve integration and interoperability among several Workflow Management Systems and Problem Solving Environments (PSE) in order to realize a Medical Image Analysis Support System at the University of Amsterdam Academisch Medical Centrum, Amsterdam.\\
\textbf{CourseWork}\\
Distributed Stochastic Simulation, Introduction to Grid Computing, Scientific Visualization and Virtual Reality, Grid Hardware Infrastructures, Distributed Programming Methods, Profile Project -- Grid Computing (Task Farming fMRI jobs on DAS-2 Cluster using Nimrod-G and Globus), Scientific Computing on the Grid, Computational Finance, Theory and Application of Multi-Threading, Concurrent Systems.
\citem{Gujarat University}, Ahmedabad, India.\\
Masters in Computer Applications (MCA), September 2001.\\
\textbf{Major Courses}: Fundamentals of Programming, Database Systems, Operating Systems, Data and File Structures, Object Oriented Analysis and Design, Discrete Mathematical Structures, Numerical Methods, Software Engineering, Client Server Technologies, Networking Technologies, Computer Architecture.
\citem{Gujarat University}, Ahmedabad, India.\\
Bachelors in Science, June 1998.
\end{category}

\bibliographystyle{unsrt}
\renewcommand\refname{Selected Publications}
\bibliography{selectedpub}
\nocite{*}
% \includepdf[pages=1-1]{cover_letter.pdf}
\end{document}
